Implementation Design Patters for Pursuit-Evasion Problems with Bounded Speed

### 2012-12-01 paper.tex
explanation of blended paradigm
rushing this so hard

Contaminated triangles and vertices in \(G\) are meant to represent regions in \(R\) where an evader could possibly be. In that case, if a contaminated region is adjacent to an uncontaminated region, it is possible that an evader could move from the contaminated to the uncontaminated region, making both uncontaminated. This creates a degree of "spreading" contamination that needs to be kept in check by the pursuers. Since the evaders move at a bounded speed though, it can be expected that contamination does not happen necessarily instantaneously. For this reason the edges in \(G\) have a weight associated with them. Contamination from one vertex/triangle to another happens at a speed: \begin{displaymath}
foo penis
\end{displaymath}

% tesslation through barycenters
% strategic issues

>>>>

Contaminated triangles and vertices in \(G\) are meant to represent regions in \(R\) where an evader could possibly be. In that case, if a contaminated region is adjacent to an uncontaminated region, it is possible that an evader could move from the contaminated to the uncontaminated region, making both uncontaminated. This creates a degree of "spreading" contamination that needs to be kept in check by the pursuers. Since the evaders move at a bounded speed though, it can be expected that contamination does not happen necessarily instantaneously. For this reason the edges in \(G\) have a weight associated with them. Contamination from one vertex/triangle to another happens after a delay \(D\) where: \begin{displaymath}
D = \frac{\text{length of edge between vertices}}{\text{maximum bounded speed of evader(s)}}\times \text{S} ; S\in(0,1]
\end{displaymath}\(S\) represents a "shortcut" value, which can be altered to scale contamination speed/ Evaders may not necessarily go from center to center in each triangle, and could spend less time in one than expected.

An issue that may arise is evader travel time in a triangle/vertex may be less than the estimated contamination delay. An evader may only spend a moment crossing a corner of a triangle and jump ahead of the spreading contamination, for example. To help alleviate this error ahead of time, one can subdivide a triangle/vertex into three at it's barycentric center. This technique divides areas into smaller regions with faster contamination speeds, allowing for a granularity closer to \(\mathbb{R}^2\).

Strategically, pursuers can follow various techniques to capture evaders in \(R\). The first to come to mind is attempting to clear all contaminated spaces. This may be possible in some graphs, but others could have contamination that spreads faster than it can be removed. Another process is to use the theorem provided by Aigner and Fromme, if three pursuers move along the triangles akin to \(G\), slowly closing in on a potential area, they can encapsulate and close any evader in theory. We can apply this theorem due to the collection of triangles being planar and reflecting onto \(G\). This method would be irrespective of visibility if all pursuers begin in one "corner" of the polygon.
